Generalization Errors of Hard Parameter Sharing: High-dimensional Asymptotics and Implications

### 2020-09-30 arxiv/proof_gaussian_case.tex
revise

\begin{definition}[Stochastic domination]\label{stoch_domination}
Let $\xi\equiv \xi^{(n)}$ and $\zeta\equiv \zeta^{(n)}$ be two $n$-dependent random variables.
\HZ{what is $n$-dependent rv?}[{\cor Most variables in our paper are $n$-dependent implicitly, such as resolvents. Furthermore, the random matrix entries can also depend on $n$ if we want. One important example is Bernoulli random variable with sparsity $p=n^{-\theta}$. Furthermore, this also includes the random variables that do not depend on $n$ as a special case.}]
We say that $\xi$ is stochastically dominated by $\zeta$, denoted by $\xi\prec \zeta$ or $\xi=\OO_\prec(\zeta)$, if for any small constant $\e > 0$ and any large constant $D > 0$, there exists a function $n_0(\e, D)$ such that for any $n > n_0(\e, D)$,
\[ \bbP\left(|\xi| >n^\e |\zeta|\right)\le n^{-D}. \]
In case $\xi(u)$ and $\zeta(u)$ is a function of $u$ supported in $\cal U$, then we say $\xi(u)$ is stochastically dominated by $\zeta(u)$ uniformly in $\cal U$ if % for any constants $\e, D>0$,
\[ \sup_{u\in \cal U}\bbP\left(|\xi(u)|>n^\e |\zeta(u)|\right)\le n^{-D}. \]
\end{definition}

>>>>

\begin{definition}[Stochastic domination]\label{stoch_domination}
Let $\xi\equiv \xi^{(n)}$ and $\zeta\equiv \zeta^{(n)}$ be two $n$-dependent random variables.
%\HZ{what is $n$-dependent rv?}[{\cor Most variables in our paper are $n$-dependent implicitly, such as resolvents. Furthermore, the random matrix entries can also depend on $n$ if we want. One important example is Bernoulli random variable with sparsity $p=n^{-\theta}$. Furthermore, this also includes the random variables that do not depend on $n$ as a special case.}]
We say that $\xi$ is stochastically dominated by $\zeta$, denoted by $\xi\prec \zeta$ or $\xi=\OO_\prec(\zeta)$, if for any small constant $\e > 0$ and any large constant $D > 0$, there exists a function $n_0(\e, D)$ such that for any $n > n_0(\e, D)$,
\[ \bbP\left(|\xi| >n^\e |\zeta|\right)\le n^{-D}. \]
In case $\xi(u)$ and $\zeta(u)$ is a function of $u$ supported in $\cal U$, then we say $\xi(u)$ is stochastically dominated by $\zeta(u)$ uniformly in $\cal U$ if % for any constants $\e, D>0$,
\[ \sup_{u\in \cal U}\bbP\left(|\xi(u)|>n^\e |\zeta(u)|\right)\le n^{-D}. \]
\end{definition}
